%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Work Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Lead Backend Engineer} % Job title
    {Onuii(설탭)} % Organization
    {Seoul, S.Korea} % Location
    {Mar. 2022 - Now} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Fostered team growth through one-on-one meetings, resulting in an average skill level increase across 14 team members.}
        \item {Deployed Kakfa echo system with golang, including consumer proxy, producer, monitoring, to establish an event-driven architecture.}
        \item {Implemented a GraphQL gateway for efficient request handling to gRPC services, enhancing endpoint integration and caching. Customizing graphql-mesh, using explicit optional in protobuf3 to handle graphql nullable.}
        \item {Designed Data pipeline to make a data lake using AWS EKS,EMR, Trino, Datahub, Spark.}
        \item {Provisioned microservice infrastructure using AWS ECS, ECR, and Service Connect discovery, employing IaC tools like Packer and Terraform for seamless deployment.}
        \item {Transitioned from monolithic and serverless legacy systems to a microservice architecture using Kafka and gRPC for service discovery.}
        \item {Developed a teacher-student matching algorithm, leveraging AWS Opensearch for data analysis based on sensitive student information.}
        \item {Introduced "Risk Search" as a proactive measure in the development process.}
        \item {Utilized Post-mortem analyses to create a historical knowledge base for domain-related issues.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {CTO} % Job title
    {Flatgarden} % Organization
    {Seoul, S.Korea} % Location
    {Mar. 2020 - Mar. 2022} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Deployed "입시 고민 메신저 학학이" in App store and google play}
        \item {Built infrastructure utilizing Docker and Terraform with AWS ECS in AWS architecture and migrated legacy to ecs fargate}
        \item {Designed real-time chat bot with Firebase FireStore for scalable service.}
        \item {Implemented modified scrum by using zenhub, notion to effectively communicate}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Graduate Student Researcher} % Job title
    {Seoul National University of Science and Technology} % Organization
    {Seoul, S.Korea} % Location
    {May. 2019 - Feb. 2022} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Implemented TPC-C Benchmark(WAS, RTE, DB) on IBM DB2 using C, Golang with TTA(Telecommunications Technology Association)}
        \item {Developed an Intelligent (AI) Small Water Utility Integrated Management System with Kafka, Telegraf with Kafka Connect, InfluxDB, Grafana with WonJu-si}
        \item {Implemented a complete and fast Scraping method for collecting tweets with NSR(National Security Researcher Institute) }
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Software Engineer} % Job title
    {Hyundai-Medi} % Organization
    {Seoul, S.Korea} % Location
    {DEC. 2018 - MAR. 2019} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Implemented Hospital and Pharmacy Search service using Python Django rest framework.}
        \item {Crawled medicine information}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Software Engineer} % Job title
    {Playauto} % Organization
    {Seoul, S.Korea} % Location
    {AUG. 2017 - NOV. 2018} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Implemented data scraping of E-Commerce service like Coupang, G-market for automating registering goods and inventory management }
        \item {Developed an inventory management system for enterprise customer}
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}
